\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} %corrects accents
\usepackage[margin=1.0in]{geometry}
\usepackage[colorlinks=true,
            urlcolor=blue,
            pdfauthor={Ithallo Junior Alves Guimaraes},
            pdftitle={CV de Ithallo},
            ]{hyperref}
\usepackage{scrextend} %addmargin
\usepackage{multicol} % multiline columns for itemize
\setlength{\parindent}{0cm}

\begin{document}

\begin{center}
\huge{Ithallo Junior Alves Guimarães}
\end{center}

\section{Personal Information}
\hrule \vspace{0.1cm}

\begin{addmargin}{0.5cm}

%\textbf{Endereço:}  Riacho Fundo 1, Brasília - DF. \\
\textbf{Address}: Brasilia, DF, Brazil \\
% \textbf{Telefone:}  +55 61 99951-7324 \\
\textbf{Email:}   \href{maito:ithallojunior@outlook.com}{ithallojunior@outlook.com} \\
\textbf{GitHub:} \url{https://github.com/ithallojunior} \\
\textbf{Linkedin:} \url{https://linkedin.com/in/ithallo/}

\end{addmargin}

\section{Introduction}
\hrule \vspace{0.1cm}

\begin{addmargin}{0.5cm}
Python  and Go/Golang developer with an MSc of Biomedical Engineering and an Electronics Engineering background.
Experienced with Python, Go/Golang, Docker, Kubernetes, Machine Learning, 
biomedical (and electronic) instrumentation, biomedical signal 
acquisition, digital signal processing, and others. Self-taught, committed, and a fast learner. I natively speak Portuguese,
basic Spanish and basic French, and I'm fluent in English.

\end{addmargin}

\section{Formal Education:}
\hrule \vspace{0.1cm}

\textbf{2018 - 2021}
\begin{addmargin}{0.5cm}
Master's degree in Biomedical Engineering - University of Brasilia (UnB), Brasilia, Brazil. \\
% Master's thesis subject: Development of a wireless surface electromyography device and comparison to the Delsys Bagnoli \\
\end{addmargin}

\textbf{2012 - 2017}
\begin{addmargin}{0.5cm}
Bachelor's degree in Electronics Engineering - University of Brasilia (UnB), Brasilia, Brazil. \\
\end{addmargin}

\textbf{2014 - 2015}
\begin{addmargin}{0.5cm}
Exchange Student (Electrical Engineering) - Budapest University of Technology and Economics (BME), Budapest, Hungary.
\end{addmargin}

\section{Work Experience:}
\hrule \vspace{0.1cm}

\textbf{September 2021 - present day}
\begin{addmargin}{0.5cm}
Senior Software Analyst - Eldorado Research Institute\\
Worked on different projects as:
\begin{itemize}
    \item Tech lead and developer. Technologies: Python (PyQt, Flask e SQLAlchemy), Microsoft SQL Server, SQLite, Docker, and embedded linux.
    \item Developer. Technologies: Go/Golang (Operator-SDK), Docker, Kubernetes, Prometheus, Grafana, and TimescaleDB. \\
\end{itemize}
\end{addmargin}

\newpage
\textbf{May 2021 - September 2021}
\begin{addmargin}{0.5cm}
Software Analyst - Eldorado Research Institute \\
Tech lead and developer. Technologies: Python (PyQt, Flask e SQLAlchemy), Microsoft SQL Server, SQLite, Docker, and embedded linux.\\
\end{addmargin}

\textbf{December 2020 - May 2021}
\begin{addmargin}{0.5cm}
    Systems Analyst I - Coopersystem \\
    Main Python back-end developer for the Portal Coopersystem project with the following technologies: Django, Django REST Framework, Celery, RabbitMQ, PostgreSQL, and Docker.\\
\end{addmargin}

\textbf{September 2019 - December 2020}
\begin{addmargin}{0.5cm}
Programmer II - Coopersystem.\\
Main Python back-end developer for the Portal Coopersystem project with the following technologies: Django, Django REST Framework, Celery, RabbitMQ, PostgreSQL, and Docker.\\
\end{addmargin}

% \textbf{January 2019 - present day}
% \begin{addmargin}{0.5cm}
% Private teacher.\\
% Review lessons on academic subjects, such as calculus, digital electronics, and 
% programming and writing of high school supplemental material.\\
% \end{addmargin}

\textbf{March 2018 - September 2019}
\begin{addmargin}{0.5cm}
Scholarship Holder - Coordenadoria de Aperfeiçoamento de Pessoal de Nível Superior (CAPES). \\
Scholarship holder of the Postgraduate Program in Biomedical Engineering of the
Gama Faculty, University of Brasilia (PPGEB FGA-UnB).\\
Research field: Analysis and development of health and intelligent systems.\\
\end{addmargin}

\textbf{October 2018 - December 2018}
\begin{addmargin}{0.5cm}
Voluntary Teacher -  Gama Faculty, University of Brasilia (FGA-UnB).\\
Teacher of the Laboratory of Digital Electronics 1 course. \\
\end{addmargin}

\textbf{March 2018 - July 2018}
\begin{addmargin}{0.5cm}
Teaching Intern - Gama Faculty, University of Brasilia (FGA-UnB).\\
Lectures given on the Artificial Intelligence  course  about Artificial Neural Networks
and Genetic Algorithms. \\
\end{addmargin}

\textbf{September 2017 - February 2018}
\begin{addmargin}{0.5cm}
Python developer (intern) - LoopKey.\\
Development of communication, automation, and control systems via Bluetooth on
embedded Linux systems with Python. \\
\end{addmargin}

\textbf{January 2017 - December 2017}
\begin{addmargin}{0.5cm}
Voluntary research intern.\\
Voluntary research intern for the Laboratory of Health Informatics
(Laboratório de Informática em Saúde - LIS) of the University of
Brasilia (UnB) on the project of technological development for the adaptation of artificial limbs on transfemural amputees, working with electronics circuit design, Python, and applied Machine Learning models. \\
\end{addmargin}

\newpage
\textbf{January 2016 - January 2017}
\begin{addmargin}{0.5cm}
Research Intern - Fundação de Apoio a Pesquisa do Distrito Federal (FAP-DF).\\
Scientific scholarship holder for the Laboratory of Health Informatics
(Laboratório de Informática em Saúde - LIS) of the University of
Brasilia (UnB) on the project of technological development for the adaptation of artificial
limbs on transfemural amputees, working with electronics circuit design, Python, and applied
Machine Learning models. \\

\end{addmargin}

\textbf{September 2014 - August 2015}
\begin{addmargin}{0.5cm}
Scholarship Holder - Coordenadoria de Aperfeiçoamento de Pessoal de Nível Superior (CAPES). \\
Exchange student and scholarship holder for the Science without Borders program of the Brazilian
Government on the Budapest University of Technology and Economics (BME). \\
\end{addmargin}

\section{Skills:}
\hrule \vspace{0.1cm}

\subsection{Languages:}
\begin{center}
\begin{tabular}{c | c | c | c}
\hline
\textbf{Language:} & Speaking  & Reading & Writing \\
\hline
\hline
\textbf{Portuguese} &  Native & Native & Native  \\
\hline
\textbf{Inglês} &  Fluent & Fluent & Fluent  \\
\hline
\textbf{Spanish} & Basic & Basic & Basic \\
\hline
\textbf{French} & Basic & Basic & Basic \\
\hline
\end{tabular}
\end{center}

\subsection{General skills:}
\begin{multicols}{3} %number of columns
    \begin{itemize}
        \item Python;
        \item Go/Golang;
        \item C;
        \item Shell script;
        \item Git;
        \item Gitflow;
        \item Docker;
        \item Kubernetes;
        \item PostgreSQL;
        \item C\#;
        \item \textit{Machine Learning};
        \item \LaTeX ;
        \item Matlab;
        \item Octave;
        \item Julia;
        \item Celery;
        \item RabbitMQ
        % \item Office (Word, Excel e PowerPoint);
        % \item LibreOffice;
        % \item Pages, Numbers e Keynote;
        % \item Windows, GNU/Linux e MacOS;
        \item Biomedical signal acquisition;
        \item Electronics and biomedical instrumentation;
        \item Analog and digital filtering;
        \item Arduino;
        \item Digital signal processing;
        \item Bot programming.
    \end{itemize}
\end{multicols}


\end{document}
